Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species

### 2017-02-14 ms/Accessory/Wenk-Accessory-SI.Rnw
Fix errors in building suppmat

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
  accessory_vs_RE <- lines(fit$groupsummary)
  accessory_vs_RE <- dplyr::select(accessory_vs_RE,group,n,r2,pval)

@@

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
  accessory_vs_size <- lines(fit$groupsummary)
  accessory_vs_size <- dplyr::select(accessory_vs_size,group,n,r2,pval)

@@

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
  accessory_vs_age <- lines(fit$groupsummary)
  accessory_vs_age <- dplyr::select(accessory_vs_age,group,n,r2,pval)

@@

acc_by_species$r2 <- format(acc_by_species$r2,digits=2)
acc_by_species$pval <- format_p(acc_by_species$pval)
acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=2)
acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
}
TableS19 <- make_table_Table2_using_propagule()
@
\begin{table}[H]
\centering
\caption{Scaling of reproductive tissue costs with total propagule size}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.94cm}x{3cm}x{1.5cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS19)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
  TableS18 <- lines(fit$groupsummary)
  TableS18 <- dplyr::select(TableS18,group,n,r2,pval)

@@

\begin{table}[H]
\centering
\caption{Count of buds initiated is well predicted by plant size}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS18)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

\subsection{investment categories by species}
List for each species of reproductive tissue types included in each of the investment categories
<<echo=FALSE,results='asis'>>=
  @@@("../../data/accessoryParts.yml")
@

@@

accessory_parts.yml
flowerCategories.csv and flowerCategories_meta.csv
flowerParts.csv and flowerParts_meta.csv
individuals.csv and individuals_meta.csv
MultiplierTable.csv
reproduction.csv and reproduction_meta.csv
seedMultiplier.csv

The following files contain supplmentary data about the species and sites:
seedsize.csv and seedsize_meta.csv
sites.csv and sites_meta.csv
species.csv

>>>>

\begin{document}

@@

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
  accessory_vs_RE <- dplyr::select(fit$groupsummary,group,n,r2,pval)

@@

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
  accessory_vs_size <- dplyr::select(fit$groupsummary,group,n,r2,pval)

@@

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
  accessory_vs_age <- dplyr::select(fit$groupsummary,group,n,r2,pval)

@@

acc_by_species$r2 <- format(acc_by_species$r2,digits=2)
acc_by_species$pval <- format_p(acc_by_species$pval)
acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=2)
acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
}
TableS19 <- make_table_Table2_using_propagule()
@
\begin{table}[H]
\centering
\caption{Scaling of reproductive tissue costs with total propagule size}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.94cm}x{3cm}p{1.5cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS19)
        # , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
  TableS18 <- dplyr::select(fit$groupsummary,group,n,r2,pval)

@@

\begin{table}[H]
\centering
\caption{Count of buds initiated is well predicted by plant size}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.94cm}x{1cm}p{1.5cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS18)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

\subsection{investment categories by species}
List for each species of reproductive tissue types included in each of the investment categories
<<echo=FALSE,results='asis'>>=
  ###("../../data/accessoryParts.yml")
@

@@

accessory\_parts.yml
flowerCategories.csv and flowerCategories\_meta.csv
flowerParts.csv and flowerParts\_meta.csv
individuals.csv and individuals\_meta.csv
MultiplierTable.csv
reproduction.csv and reproduction\_meta.csv
seedMultiplier.csv

The following files contain supplmentary data about the species and sites:
seedsize.csv and seedsize\_meta.csv
sites.csv and sites\_meta.csv
species.csv
